Enhancing Forecast Reconciliation: A Study of Alternative Covariance Estimators

### 2025-07-04 literature/paper_draft.qmd
small fix

Traditionally, forecasting these hierarchical time series has been done using single-level methods, such as bottom-up, top-down, and middle-out approaches. Bottom-up methods involve generating forecasts for the bottom-level series and aggregating them to higher levels. Top-down methods start with forecasts for the only top level and disaggregate them down. Middle-out methods combine both approaches by forecasting a middle level and then aggregating or disaggregating as needed. Despite their simplicity, these methods only anchor forecasts to a single level, implying a large loss of information on the hierarchy's inherent correlation structure. Furthermore, as we will see in @sec-hierarchy, the disaggregation becomes more complex when structure is grouped since the disaggregation paths are not unique.

>>>>

Traditionally, forecasting these hierarchical time series has been done using single-level methods, such as bottom-up, top-down, and middle-out approaches. Bottom-up methods involve generating forecasts for the bottom-level series and aggregating them to higher levels. Top-down methods start with forecasts for the only top level and disaggregate them down. Middle-out methods combine both approaches by forecasting a middle level and then aggregating or disaggregating as needed. Despite their simplicity, these methods only anchor forecasts to a single level, implying a large loss of information on the hierarchy's inherent correlation structure. Furthermore, as we saw from the Starbucks example considering the sales of different kinds of drinks at each aggregation level -- formally defined as grouped structure in @sec-hierarchy -- the disaggregation becomes more complex since the disaggregation paths are not unique.
